Probability

### 2016-04-30 prob.tex
small comments

We will return to finite set-valued probability measures in Sec.~\ref{sec:?}.

\paragraph*{Interval-valued probability measures.} In this case, we
split the $[0,1]$ interval into a collection of closed sub-intervals
obeying certain restrictions to be described at the end of the
section. To illustrate the main ideas, we first consider a simple
example.

\begin{example}[Two-coin probability space with four intervals]
We split the interval in the following four closed sub-intervals:
\begin{itemize}
\item $[0,0]$ which we call \imposs, 
\item $[0,\frac{1}{2}]$ which we call \unlikely, 
\item $[\frac{1}{2},1]$ which we call \likely, and 
\item $[1,1]$ which we call \necess.
\end{itemize}
The probability measure in this case becomes:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Not only does this probability measure reveal that the second coin is
double-headed but it also reveals that the first coin is more likely
to be heads than tails, despite the absence of numeric information.
\qed\end{example}

@@

\yutsung{Although this is clearer than the previous one, I keep some
intervals instead write everything in \imposs, \unlikely, \likely,
and \necess. The biggest point is the addition rule~$\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$:
\begin{itemize}
\item This rule without \overflow will be push complexity to ``we may abort
computing probability when....''
\item It seems more concisely than a table among \imposs, \unlikely, \likely,
and \necess.
\end{itemize}
However, if you prefer as less interval as possible, I may try to
replace them by \imposs, \unlikely, \likely, and \necess...}

@@

>>>>

\paragraph*{Interval-valued probability measures.} In this case, we
split the $[0,1]$ interval into a collection of overlapping closed
sub-intervals obeying certain restrictions to be described at the end
of the section. To illustrate the main ideas, we first consider a
simple example.

\begin{example}[Two-coin probability space with four intervals]
We split the interval in the following four closed sub-intervals:
\begin{itemize}
\item $[0,0]$ which we call \imposs, 
\item $[0,\frac{1}{2}]$ which we call \unlikely, 
\item $[\frac{1}{2},1]$ which we call \likely, and 
\item $[1,1]$ which we call \necess.
\end{itemize}
Using these new values, the probability measure becomes:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Not only does this probability measure reveal that the second coin is
double-headed but it also reveals that the first coin is more likely
to be tails than heads, despite the absence of numeric information.
\qed\end{example}

@@

\yutsung{Although this is clearer than the previous one, I keep some
intervals instead write everything in \imposs, \unlikely, \likely,
and \necess. The biggest point is the addition rule~$\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$:
\begin{itemize}
\item This rule without \overflow will be push complexity to ``we may abort
computing probability when....''
\item It seems more concisely than a table among \imposs, \unlikely, \likely,
and \necess.
\end{itemize}
However, if you prefer as less interval as possible, I may try to
replace them by \imposs, \unlikely, \likely, and \necess...}
\amr{I like this. We just might need to rewrite a little but overall
  it's good.}

@@

\amr{Here it would be good to refer to the notion of ``quantum test''
  and define events as sums of quantum tests. This will automatically
  include everything except the products of commutative projections
  which we will have to explain that they can be expressed as sums of
  orthogonal projections.}
